\plaintitle

### 2017-08-22 docs/papers/IARPA-RFI-17-03/rfi.tex
updated the layout

\usepackage[breaklinks,hidelinks]{hyperref}

\title{SDC: Social Dispersed Computing}
\date{}
\begin{document}
\maketitle

@@

The classic Internet architecture assumes computing hosts whose task is to perform computations
and a network of switches and routers whose sole task is to route network packets. This architecture delegates all computing to end-nodes and all communications to the network. However, every resource (node or edge) in this architecture has a finite capacity potentially leading to inefficient allocation of resources to communications and computations.  This is the networking model on which our current state-of-the-art cloud computing architectures are built. While this is sufficient for most tasks, it does not scale up when we try to use this architecture in the new emerging paradigm of Digitalization. In this new paradigm, the boundaries between the network node, the sensor, and the actuator are blurring, driven primarily by the Internet of Things and the smartphone revolution. The data generated via this network is extremely large and needs clever, scalable, and possibly decentralized computing solutions that can scale independently as required. In this network, any node in the graph can serve as a computing or network
router node (or both), and  the complex application can possibly be distributed over the network
of these nodes, so that the overall performance (e.g., amount of data processed over
time) is significantly improved.  This is the concept behind `Social Dispersed Computing,' on which our group has been working. In this whitepaper, we describe two use-cases for this new computing paradigm and describe the challenges which must be solved.

@@

\clearpage
\section{Description}
The existing Internet architecture was envisioned more than 30 years ago. This architecture relies on separate computing and communication resources: computing hosts on the edge communicate via a network whose task is to route and deliver network packets as efficiently as possible. This strict separation of computation from communication has its drawbacks: for instance, computations that reduce large datasets (arriving from other hosts) to smaller ones (that are needed by another group of hosts) are going to be inefficient, due to the limits of network communication. However, it would often be more efficient to move the computation `closer' to the source hosts and then just send the results to the target hosts. A specific example is that of sensor processing: target recognition in sensor streams should be done as close to the source as possible, because doing it somewhere else would incur performance penalties.  Arguably, this is possible today but on an ad-hoc basis. Careful management and deployment of application software components over a network of `owned' nodes can be done with a great deal of manual and error-prone operations. These solutions are brittle, labor intensive, and not responsive enough to rapid changes in the network or the utilization of computing hosts.

@@

\subsubsection{Privacy Problem}

@@

\subsubsection{Privacy Problem}
A solution to this problem requires a social computing and information sharing platform that overcomes the incentive gap between individuals and municipalities. This platform must offer mixed-mode routing suggestions and general system information to travelers and---in turn---supply service providers with high-fidelity information about how users are consuming different transportation resources. At the same time, this system must also consider the investment required by the cities in the computing infrastructure required to solve the problem at scale. Alternatively, a social dispersed computing approach that utilizes the various edge computing resources available in the city, including the mobile devices of the commuters, can be employed by municipalities to improve efficiency within their cities with little investment.

>>>>

\usepackage[breaklinks,hidelinks]{hyperref}
\usepackage{pdfpages}

\title{SDC: Social Dispersed Computing}
\date{}
\begin{document}

\includepdf[pages=-]{coverpage.pdf}

\maketitle

@@

The classic Internet architecture assumes computing hosts whose task is to perform computations
and a network of switches and routers whose sole task is to route network packets. This architecture delegates all computing to end-nodes and all communications to the network. However, every resource (node or edge) in this architecture has a finite capacity potentially leading to inefficient allocation of resources to communications and computations.  This is the networking model on which our current state-of-the-art cloud computing architectures are built. While this is sufficient for most tasks, it does not scale up when we try to use this architecture in the new emerging paradigm of Digitalization. In this new paradigm, the boundaries between the network node, the sensor, and the actuator are blurring, driven primarily by the Internet of Things and the smartphone revolution. The data generated via this network is extremely large and needs clever, scalable, and possibly decentralized computing solutions that can scale independently as required. In this network, any node in the graph can serve as a computing or network
router node (or both), and  the complex application can possibly be distributed over the network
of these nodes, so that the overall performance (e.g., amount of data processed over
time) is significantly improved.  This is the concept behind `Social Dispersed Computing,' on which our group has been working. 
Blockchain based computational platforms may act as a key enabling technology for social dispersed computing, by solving the above coordination problem. 
To enable the next step in the evolution of decentralized computing, blockchain platforms must be extended with functionality that allows them to perform computations on encrypted variables.
In this direction, homomorphic encryption can act as an enabling technology. In this whitepaper, we describe two use-cases for this new computing paradigm and describe the challenges which must be solved.

@@

\thispagestyle{empty}

\clearpage
\pagenumbering{arabic} 
\section{Description}
The existing Internet architecture was envisioned more than 30 years ago. This architecture relies on separate computing and communication resources: computing hosts on the edge communicate via a network whose task is to route and deliver network packets as efficiently as possible. This strict separation of computation from communication has its drawbacks: for instance, computations that reduce large datasets (arriving from other hosts) to smaller ones (that are needed by another group of hosts) are going to be inefficient, due to the limits of network communication. However, it would often be more efficient to move the computation `closer' to the source hosts and then just send the results to the target hosts. A specific example is that of sensor processing: target recognition in sensor streams should be done as close to the source as possible, because doing it somewhere else would incur performance penalties.  Arguably, this is possible today but on an ad-hoc basis. Careful management and deployment of application software components over a network of `owned' nodes can be done with a great deal of manual and error-prone operations. These solutions are brittle, labor intensive, and not responsive enough to rapid changes in the network or the utilization of computing hosts.

@@

\subsubsection{Challenges}

@@

\subsubsection{Challenges}
A solution to this problem requires a social computing and information sharing platform that overcomes the incentive gap between individuals and municipalities. This platform must offer mixed-mode routing suggestions and general system information to travelers and---in turn---supply service providers with high-fidelity information about how users are consuming different transportation resources. At the same time, this system must also consider the investment required by the cities in the computing infrastructure required to solve the problem at scale. Alternatively, a social dispersed computing approach that utilizes the various edge computing resources available in the city, including the mobile devices of the commuters, can be employed by municipalities to improve efficiency within their cities with little investment.

### 2017-08-22 docs/papers/IoT2017/prelim.tex
updated the layout

Figure~\ref{fig:softwareArchitecture} shows a decentralized
transactive microgrid with PETra.  In this figure, components marked
red are introduced to provide privacy in a safe and secure manner,
whereas components marked in blue are typical elements of a
decentralized transactive microgrid.
\begin{figure}[h!]
\center
\begin{tikzpicture}[x=8cm, y=0.7cm, font=\small,
  nodeStyle/.style={rounded corners=0.1cm, drop shadow={shadow xshift=0.05cm, shadow yshift=-0.05cm, fill=black}}
]
\draw [nodeStyle, fill=red!10]  (0, 1.65) rectangle    (1, 2.25) node [midway, align=center] {Communication anonymity (e.g., onion routing)};

@@

\draw [nodeStyle, fill=red!10] (0, 4.2) rectangle (0.49, 5.1) node [midway, align=center] {Anonymous trading\\[-0.2em]workflow for prosumers};
\draw [nodeStyle, fill=blue!10] (0.51, 4.2) rectangle (1, 5.1) node [midway, align=center] {Microgrid controller};
\end{tikzpicture}
\caption{Architecture of a Decentralized Transactive Microgrid with PETra.}
\label{fig:softwareArchitecture}
\end{figure}

>>>>

\begin{figure}[h!]
\center
\begin{tikzpicture}[x=8cm, y=0.7cm, font=\small,
  nodeStyle/.style={rounded corners=0.1cm, drop shadow={shadow xshift=0.05cm, shadow yshift=-0.05cm, fill=black}}
]
\draw [nodeStyle, fill=red!10]  (0, 1.65) rectangle    (1, 2.25) node [midway, align=center] {Communication anonymity (e.g., onion routing)};

@@

\draw [nodeStyle, fill=red!10] (0, 4.2) rectangle (0.49, 5.1) node [midway, align=center] {Anonymous trading\\[-0.2em]workflow for prosumers};
\draw [nodeStyle, fill=blue!10] (0.51, 4.2) rectangle (1, 5.1) node [midway, align=center] {Microgrid controller};
\end{tikzpicture}
\caption{Architecture of a decentralized transactive microgrid with \mbox{PETra}.}
\label{fig:softwareArchitecture}
\end{figure}

Figure~\ref{fig:softwareArchitecture} shows a decentralized
transactive microgrid with PETra.  
In this figure, components marked in blue are basic elements of the decentralized transactive microgrid,
while components marked in red are added (or extended) by PETra.

### 2017-08-22 docs/papers/IoT2017/related.tex
updated the layout

Other approaches, such as additional hardware components, have also been explored 
for potential privacy gains. 
Varodayan and Khisti study using a
rechargeable battery for partially protecting the privacy of
information contained in a household's electrical load
profile~\cite{varodayan2011smart}. They show that stochastic battery
policies may leak 26\% less information than a best-effort policy,
which holds the output load constant whenever possible. Tan et
al.\ study privacy in a smart metering system from an information
theoretic perspective in the presence of energy harvesting and storage
units~\cite{tan2013increasing}. They show that energy harvesting
provides increased privacy by diversifying the energy source, while a
storage device can be used to increase  energy efficiency and
privacy.
% They show that there exists a trade-off between the information
% leakage rate and the wasted energy rate, and study the impact of the
% energy harvesting rate and the size of the storage device on this trade-off.

>>>>

Other approaches, such as additional hardware components, have also been explored 
for potential privacy gains. 
Varodayan and Khisti study using a
rechargeable battery for partially protecting the privacy of
information contained in a household's electrical load
profile~\cite{varodayan2011smart}. They show that stochastic battery
policies may leak 26\% less information than a best-effort policy,
which holds the output load constant whenever possible. Tan et
al.\ study privacy in a smart metering system from an information
theoretic perspective in the presence of energy harvesting and storage
units~\cite{tan2013increasing}. They show that energy harvesting
provides increased privacy by diversifying the energy source, while a
storage device can be used to increase both energy efficiency and
privacy.
% They show that there exists a trade-off between the information
% leakage rate and the wasted energy rate, and study the impact of the
% energy harvesting rate and the size of the storage device on this trade-off.
